Testing Set Features Visualization

### 2022-11-01 TestingPipeline/Scripts/combining_tool_output.Rmd
Stats for RefSeq vs NonRefSeq viral recovery.

# VirSorter2
viruses$viral[is.na(viruses$viral)] <- 0
viruses$hallmark[is.na(viruses$hallmark)] <- 0
viruses$RNA[is.na(viruses$RNA)] <- 0
viruses$lavidaviridae[is.na(viruses$lavidaviridae)] <- 0
viruses$NCLDV[is.na(viruses$NCLDV)] <- 0
viruses$ssDNA[is.na(viruses$ssDNA)] <- 0
viruses$dsDNAphage[is.na(viruses$dsDNAphage)] <- 0

>>>>

# VirSorter2
viruses$viral[is.na(viruses$viral)] <- 0
viruses$hallmark[is.na(viruses$hallmark)] <- 0
viruses$RNA[is.na(viruses$RNA)] <- 0
viruses$lavidaviridae[is.na(viruses$lavidaviridae)] <- 0
viruses$NCLDV[is.na(viruses$NCLDV)] <- 0
viruses$ssDNA[is.na(viruses$ssDNA)] <- 0
viruses$dsDNAphage[is.na(viruses$dsDNAphage)] <- 0
viruses$viral[is.na(viruses$max_score)] <- 0

### 2022-11-01 TestingPipeline/Scripts/comparing_methods_visualization.Rmd
Stats for RefSeq vs NonRefSeq viral recovery.

>>>>

# Comparing RefSeq vs VS2 database
VS2 sequences used: (/scratch/kwigg_root/kwigg/hegartyb/VSTE/non-refseq-genomes/NCLDV/env/NCLDV_env.fna /scratch/kwigg_root/kwigg/hegartyb/VSTE/non-refseq-genomes/lavidaviridae/env/HQ_virophages.fna /scratch/kwigg_root/kwigg/hegartyb/VSTE/non-refseq-genomes/dsDNAphage/env/* /scratch/kwigg_root/kwigg/hegartyb/VSTE/non-refseq-genomes/dsDNAphage/provirus/VirSorterCuratedDataset_HQ_contigs.fna)

```{r}
refseq_vir <- read_tsv("../IntermediaryFiles/refseq_viral_genome_ids.txt",col_names = F)
refseq_vir$X1 <- sub(">", "", refseq_vir$X1)
refseq_vir <- separate(refseq_vir, col=X1, sep=" ", remove=T, into="id")
refseq_vir$id <- sub("\\.", "_", refseq_vir$id)
```

```{r}
table(refseq_vir$id %in% viruses$contig)
```

```{r}
viruses_refseq_vir <- viruses[viruses$contig %in% refseq_vir$id,]
viruses_not_refseq_vir <- viruses[!(viruses$contig %in% refseq_vir$id) & viruses$seqtype=="virus",]
```

```{r}
table(viruses_refseq_vir$max_score_group)
table(viruses_not_refseq_vir$max_score_group)
```
recall
```{r}
length(grep("true positive", viruses_refseq_vir$confusion_matrix_high_MCC))/nrow(viruses_refseq_vir)
```

```{r}
length(grep("true positive", viruses_not_refseq_vir$confusion_matrix_high_MCC))/nrow(viruses_not_refseq_vir)
```

### 2022-11-01 TestingPipeline/Scripts/rule_tuning_2022.09.06.Rmd
Stats for RefSeq vs NonRefSeq viral recovery.

  if (include_virsorter2) {
    keep_score[input_seqs$viral>=50] <- keep_score[input_seqs$viral>=50] + 0.5
    keep_score[input_seqs$viral>=95] <- keep_score[input_seqs$viral>=95] + 0.5
    keep_score[input_seqs$RNA>=0.9] <- keep_score[input_seqs$RNA>=0.9] + 1
    keep_score[input_seqs$lavidaviridae>=0.9] <- keep_score[input_seqs$lavidaviridae>=0.9] + 1
    keep_score[input_seqs$NCLDV>=0.9] <- keep_score[input_seqs$NCLDV>=0.9] + 1
  }

@@

  if (include_tuning_not_viral) {
    keep_score[input_seqs$Kaiju_Viral=="cellular organisms"] <- keep_score[input_seqs$Kaiju_Viral=="cellular organisms"] - 0.5
    keep_score[input_seqs$checkv_host_genes>50 & !input_seqs$provirus] <- keep_score[input_seqs$checkv_host_genes>50 & !input_seqs$provirus] - 1
    keep_score[input_seqs$checkv_viral_genes==0 & input_seqs$checkv_host_genes>=1] <- keep_score[input_seqs$checkv_viral_genes==0 & input_seqs$checkv_host_genes>=1] - 1
    keep_score[((input_seqs$checkv_viral_genes*3) <= input_seqs$checkv_host_genes) & !input_seqs$provirus] <- keep_score[((input_seqs$checkv_viral_genes*3) <= input_seqs$checkv_host_genes) & !input_seqs$provirus] - 1 # consider accounting for RNA viruses
    keep_score[input_seqs$checkv_length>500000 & input_seqs$hallmark<=1] <- keep_score[input_seqs$checkv_length>500000 & input_seqs$hallmark<=1] - 1
    keep_score[input_seqs$checkv_completeness<=75 & input_seqs$checkv_length<=5000] <- keep_score[input_seqs$checkv_completeness<=75 & input_seqs$checkv_length<=5000] - 0.5 # helped with protist contamination
  }

@@

## Visualize how the precision, recall, and F1 scores change across pipelines.
```{r}
pal <- ggthemes::tableau_color_pal(palette="Tableau 10", type="regular")
p2 <- ggplot(accuracy_scores, aes(x=toolcombo, y=F1, 
                                  color=numtools, fill=numtools)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (tv, DVF, tnv, VB, VS, VS2)") +
  ylab("F1 Score")
p2
ggplot(accuracy_scores, aes(x=toolcombo, y=precision, 
                                  color=numtools, fill=numtools)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (tv, DVF, tnv, VB, VS, VS2)") +
  ylab("Precision")
ggplot(accuracy_scores, aes(x=toolcombo, y=recall, 
                                  color=numtools, fill=numtools)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (tv, DVF, tnv, VB, VS, VS2)") +
  ylab("Recall")
ggplot(accuracy_scores, aes(x=precision, y=recall, 
                                  color=numtools, fill=numtools)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Precision") +
  ylab("Recall")
ggplot(accuracy_scores, aes(x=toolcombo, y=abs(precision-recall), 
                                  color=numtools, fill=numtools)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (tv, DVF, tnv, VB, VS, VS2)") +
  ylab("Precision-Recall")
ggplot(accuracy_scores, aes(x=toolcombo, y=MCC, 
                                  color=numtools, fill=numtools)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (tv, DVF, tnv, VB, VS, VS2)") +
  ylab("MCC")
ggplot(accuracy_scores, aes(x=toolcombo, y=AUC, 
                                  color=numtools, fill=numtools)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (tv, DVF, tnv, VB, VS, VS2)") +
  ylab("AUC")
ggplot(accuracy_scores, aes(x=toolcombo, y=fungal_FP, 
                                  color=numtools, fill=numtools)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (tv, DVF, tnv, VB, VS, VS2)") +
  ylab("Fungal False Positives")

@@

MCC <- (TP*TN-FP*FN)/sqrt(as.numeric(TP+FP)*as.numeric(TP+FN)*as.numeric(TN+FP)*as.numeric(TN+FN))
MCC
```

precision=66%, recall=91%, MCC=74%

@@

MCC <- (TP*TN-FP*FN)/sqrt(as.numeric(TP+FP)*as.numeric(TP+FN)*as.numeric(TN+FP)*as.numeric(TN+FN))
MCC
```

precision=0.94, recall=0.90, F1=0.92, MCC=0.85

>>>>

  if (include_virsorter2) {
    keep_score[input_seqs$viral>=50 | input_seqs$lavidaviridae>=0.95 | input_seqs$NCLDV>=0.95] <- keep_score[input_seqs$viral>=50 | input_seqs$lavidaviridae>=0.95 | input_seqs$NCLDV>=0.95] + 0.5
    keep_score[input_seqs$viral>=95] <- keep_score[input_seqs$viral>=95] + 0.5
    keep_score[input_seqs$RNA>=0.95] <- keep_score[input_seqs$RNA>=0.95] + 1
  }

@@

  if (include_tuning_not_viral) {
    keep_score[input_seqs$Kaiju_Viral=="cellular organisms"] <- keep_score[input_seqs$Kaiju_Viral=="cellular organisms"] - 0.5
    keep_score[input_seqs$checkv_host_genes>50 & !input_seqs$provirus] <- keep_score[input_seqs$checkv_host_genes>50 & !input_seqs$provirus] - 1
    keep_score[input_seqs$checkv_viral_genes==0 & input_seqs$checkv_host_genes>=1] <- keep_score[input_seqs$checkv_viral_genes==0 & input_seqs$checkv_host_genes>=1] - 1
    keep_score[((input_seqs$checkv_viral_genes*3) <= input_seqs$checkv_host_genes) & !input_seqs$provirus] <- keep_score[((input_seqs$checkv_viral_genes*3) <= input_seqs$checkv_host_genes) & !input_seqs$provirus] - 1 
    keep_score[input_seqs$checkv_length>500000 & input_seqs$hallmark<=1] <- keep_score[input_seqs$checkv_length>500000 & input_seqs$hallmark<=1] - 1
    keep_score[input_seqs$checkv_completeness<=75 & input_seqs$checkv_length<=5000] <- keep_score[input_seqs$checkv_completeness<=75 & input_seqs$checkv_length<=5000] - 0.5 
  }

@@

## Visualize how the precision, recall, and F1 scores change across pipelines.
```{r}
pal <- ggthemes::tableau_color_pal(palette="Tableau 10", type="regular")
p2 <- ggplot(accuracy_scores, aes(x=toolcombo, y=F1, 
                                  color=numtools, fill=numtools)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (tv, DVF, tnv, VB, VS, VS2)") +
  ylab("F1 Score")
p2
ggplot(accuracy_scores, aes(x=toolcombo, y=precision, 
                                  color=numtools, fill=numtools)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (tv, DVF, tnv, VB, VS, VS2)") +
  ylab("Precision")
ggplot(accuracy_scores, aes(x=toolcombo, y=recall, 
                                  color=numtools, fill=numtools)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (tv, DVF, tnv, VB, VS, VS2)") +
  ylab("Recall")
ggplot(accuracy_scores, aes(x=precision, y=recall, 
                                  color=numtools, fill=numtools)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Precision") +
  ylab("Recall")

ggplot(accuracy_scores[accuracy_scores$testing_set_index==1,], aes(x=precision, y=recall)) +
  geom_label(alpha=0.7, label=accuracy_scores$toolcombo[accuracy_scores$testing_set_index==1]) +
  geom_point(alpha=0.5, aes(color=numtools, fill=numtools)) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Precision") +
  ylab("Recall")

ggplot(accuracy_scores, aes(x=toolcombo, y=abs(precision-recall), 
                                  color=numtools, fill=numtools)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (tv, DVF, tnv, VB, VS, VS2)") +
  ylab("Precision-Recall")
ggplot(accuracy_scores, aes(x=toolcombo, y=MCC, 
                                  color=numtools, fill=numtools)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (tv, DVF, tnv, VB, VS, VS2)") +
  ylab("MCC")
ggplot(accuracy_scores, aes(x=toolcombo, y=AUC, 
                                  color=numtools, fill=numtools)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (tv, DVF, tnv, VB, VS, VS2)") +
  ylab("AUC")
ggplot(accuracy_scores, aes(x=toolcombo, y=fungal_FP, 
                                  color=numtools, fill=numtools)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Tool Combination (tv, DVF, tnv, VB, VS, VS2)") +
  ylab("Fungal False Positives")

@@

precision <- as.numeric(TP/(TP+FP))
precision
recall <- as.numeric(TP/(TP+FN))
recall
F1 <- as.numeric(2*precision*recall/(precision+recall))
F1

MCC <- as.numeric((TP*TN-FP*FN)/sqrt(as.numeric(TP+FP)*as.numeric(TP+FN)*as.numeric(TN+FP)*as.numeric(TN+FN)))
MCC
```

precision=69%, recall=87%, MCC=77%

@@

precision <- as.numeric(TP/(TP+FP))
precision
recall <- as.numeric(TP/(TP+FN))
recall
F1 <- as.numeric(2*precision*recall/(precision+recall))
F1

MCC <- as.numeric((TP*TN-FP*FN)/sqrt(as.numeric(TP+FP)*as.numeric(TP+FN)*as.numeric(TN+FP)*as.numeric(TN+FN)))
MCC
```

precision=0.95, recall=0.87, F1=0.91, MCC=0.82

stats for different types of sequences
```{r}
TP <- table(viruses$confusion_matrix_high_MCC)[4]
FN <- table(viruses$confusion_matrix_high_MCC)[1]

recall <- as.numeric(TP/(TP+FN))
recall
```

precision=0.95, recall=0.87, F1=0.91, MCC=0.82

```{r}
head(viruses$contig[viruses$seqtype=="virus"])
tail(viruses$contig[viruses$seqtype=="virus"])
```

### 2022-11-01 TestingPipeline/Scripts/testing_set_features_visualization.Rmd
Stats for RefSeq vs NonRefSeq viral recovery.

```{r}
plot(viruses$RNA, viruses$viral)
plot(viruses$lavidaviridae, viruses$viral)
plot(viruses$NCLDV, viruses$viral)
plot(viruses$ssDNA, viruses$viral)
```

@@

@@

keep_score[viruses$hallmark>2] <- keep_score[viruses$hallmark>2] + 1
table(keep_score, viruses$seqtype)
keep_score[viruses$checkv_host_genes>50 & viruses$checkv_provirus=="No"] <- keep_score[viruses$checkv_host_genes>50 & viruses$checkv_provirus=="No"] - 1
table(keep_score, viruses$seqtype)
keep_score[viruses$percent_unknown>=75 & viruses$checkv_length<50000] <- keep_score[viruses$percent_unknown>=75 & viruses$checkv_length<50000] + 0.5
table(keep_score, viruses$seqtype)
keep_score[viruses$percent_viral>=50] <- keep_score[viruses$percent_viral>=50] + 0.5
table(keep_score, viruses$seqtype)
    #keep_score[viruses$hallmark>=(viruses$checkv_viral_genes/5)] <- keep_score[viruses$hallmark>=(viruses$checkv_viral_genes/5)] + 1 #add some ratio
keep_score[viruses$checkv_viral_genes==0 & viruses$checkv_host_genes>=1] <- keep_score[viruses$checkv_viral_genes==0 & viruses$checkv_host_genes>=1] - 1
table(keep_score, viruses$seqtype)
keep_score[((viruses$checkv_viral_genes*3) <= viruses$checkv_host_genes) & viruses$checkv_provirus=="No"] <- keep_score[((viruses$checkv_viral_genes*3) <= viruses$checkv_host_genes) & viruses$checkv_provirus=="No"] - 1 # consider accounting for provirus designation
table(keep_score, viruses$seqtype)
#    keep_score[(viruses$checkv_viral_genes*3) <= viruses$checkv_host_genes] <- 0 # consider accounting for provirus designation
keep_score[viruses$checkv_length>500000 & viruses$hallmark==0] <- keep_score[viruses$checkv_length>500000 & viruses$hallmark==0] - 1
table(keep_score, viruses$seqtype)
```

>>>>

```{r}
ggplot(viruses, aes(x=RNA, y=viral)) +
  geom_hex(bins = 30) +
  scale_fill_continuous(type = "viridis", trans="log10") +
  theme_bw() +
  facet_wrap(~seqtype, scales = "free") +
  xlab("RNA VS2 Score") +
  ylab("VS2 Viral Score")

ggplot(viruses, aes(x=RNA, y=viral)) +
  geom_hex(bins = 30) +
  scale_fill_continuous(type = "viridis", trans="log10") +
  theme_bw() +
  facet_wrap(~confusion_matrix_high_MCC, scales = "free") +
  xlab("RNA VS2 Score") +
  ylab("VS2 Viral Score")

ggplot(viruses, aes(x=NCLDV, y=viral)) +
  geom_hex(bins = 30) +
  scale_fill_continuous(type = "viridis", trans="log10") +
  theme_bw() +
  facet_wrap(~seqtype, scales = "free") +
  xlab("NCLDV VS2 Score") +
  ylab("VS2 Viral Score")

ggplot(viruses, aes(x=NCLDV, y=viral)) +
  geom_hex(bins = 30) +
  scale_fill_continuous(type = "viridis", trans="log10") +
  theme_bw() +
  facet_wrap(~confusion_matrix_high_MCC, scales = "free") +
  xlab("NCLDV VS2 Score") +
  ylab("VS2 Viral Score")

ggplot(viruses, aes(x=lavidaviridae, y=viral)) +
  geom_hex(bins = 30) +
  scale_fill_continuous(type = "viridis", trans="log10") +
  theme_bw() +
  facet_wrap(~seqtype, scales = "free") +
  xlab("Lavidaviridae VS2 Score") +
  ylab("VS2 Viral Score")

ggplot(viruses, aes(x=lavidaviridae, y=viral)) +
  geom_hex(bins = 30) +
  scale_fill_continuous(type = "viridis", trans="log10") +
  theme_bw() +
  facet_wrap(~confusion_matrix_high_MCC, scales = "free") +
  xlab("Lavidaviridae VS2 Score") +
  ylab("VS2 Viral Score")
```

@@

```{r}
ggplot(viruses, aes(x=checkv_host_genes, y=checkv_length)) +
  geom_hex(bins = 30) +
  scale_fill_continuous(type = "viridis", trans="log10") +
  theme_bw() +
  facet_wrap(~seqtype, scales = "free") +
  xlab("Length of Sequence") +
  ylab("Number of Host Genes")
```
```{r}
table(viruses$checkv_host_genes>=50, viruses$seqtype)
```

@@

keep_score[viruses$hallmark>2] <- keep_score[viruses$hallmark>2] + 1
table(keep_score, viruses$seqtype)
keep_score[viruses$checkv_host_genes>50 & viruses$provirus=="No"] <- keep_score[viruses$checkv_host_genes>50 & viruses$provirus=="No"] - 1
table(keep_score, viruses$seqtype)
keep_score[viruses$percent_unknown>=75 & viruses$checkv_length<50000] <- keep_score[viruses$percent_unknown>=75 & viruses$checkv_length<50000] + 0.5
table(keep_score, viruses$seqtype)
keep_score[viruses$percent_viral>=50] <- keep_score[viruses$percent_viral>=50] + 0.5
table(keep_score, viruses$seqtype)
    #keep_score[viruses$hallmark>=(viruses$checkv_viral_genes/5)] <- keep_score[viruses$hallmark>=(viruses$checkv_viral_genes/5)] + 1 #add some ratio
keep_score[viruses$checkv_viral_genes==0 & viruses$checkv_host_genes>=1] <- keep_score[viruses$checkv_viral_genes==0 & viruses$checkv_host_genes>=1] - 1
table(keep_score, viruses$seqtype)
keep_score[((viruses$checkv_viral_genes*3) <= viruses$checkv_host_genes) & viruses$provirus=="No"] <- keep_score[((viruses$checkv_viral_genes*3) <= viruses$checkv_host_genes) & viruses$provirus=="No"] - 1 # consider accounting for provirus designation
table(keep_score, viruses$seqtype)
#    keep_score[(viruses$checkv_viral_genes*3) <= viruses$checkv_host_genes] <- 0 # consider accounting for provirus designation
keep_score[viruses$checkv_length>500000 & viruses$hallmark==0] <- keep_score[viruses$checkv_length>500000 & viruses$hallmark==0] - 1
table(keep_score, viruses$seqtype)
```
